---
title: "Simple document"
output: html_document
---

```{r, message=F}
library(tidyverse)
```



I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r} 
samp = rnorm(100)
length(samp)
##3 ticks: indicates r code chunk inside an Rmd file
```




# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.


# Section 3

This is going to make a plot! First I generate a dataframe, then use `ggplot` to make a scatterplot.

opt+cmd+I to make code chunk faster

{r, echo = FALSE - no code just plot}
{r, message = FALSE - no messages from execution}
{r, eval = FALSE - no plot just code}

name codechunks to keep track - can't be reused

```{r chunk_scatterplot}
plot_df <- 
  tibble(
    x = rnorm(n = 1000),
    y = 1 + 2 * x + rnorm(n = 1000)
  )

ggplot(plot_df, aes(x = x, y = y)) +
  geom_point()

```

# Section 4

This is the learning assessment!

```{r chunk_assessment}
la_df <- tibble(
  sample = rnorm(n = 500),
  positive = sample > 0,
  absolute = abs(sample)
)

ggplot(la_df, aes(x = absolute)) 
```

The median is `r round(median(la_df$absolute), 2)`.








